---
title: " ENVS-193DS Homework 03"
author: Monique Hernandez
format: html
---

[GitHub Repository](https://github.com/moniqueallyson/ENVS-193DS_homework-03.git)

```{r}
library(tidyverse)
library(gt)
library(janitor)
library(here)
mydata <- read.csv("/Users/moniquehernandez/Desktop/ENVS-193DS/assignment/hw-03/ENVS HW 3/Data.csv") |>
  clean_names()
```

## Problem 1. Personal Data

### a. Data Summarizing

I could do the mean pain level after each day to analyze if there is a comparison between the days I do yoga and the days I don't do yoga. between the days I do and don't yoga. Though, there aren't any changes for the days I don't practice yoga, so I could calculate the change in pain on days I do practice such as subtracting the pain before from the pain after to measure if yoga does help chronic pain.

### b. Visualization

```{r}

#base layer: gg plot
ggplot(mydata, aes(x = did_you_do_yoga, # x-axis
                   y = pain_level_after)) + # y-axis
  geom_jitter(height = 0, # no vertical
              width = 0.15, # narrower jitter
              color = "violet") + # color for jitter
  # scond layer: point representing mean
  stat_summary(geom = "point", # geometry being plotted
               fun = mean, # function calculating the mean
               color = "pink", #  color for average
               size = 5) + # larger point size
labs(x = "Yoga Session", # labeling x-axis
     y= "Pain Scale After Yoga") # labeling y-axis
theme_minimal()
```

### c. Caption

### d. Table presentation

## Problem 2. Affective visualization

### a. Describe affective visualization

### b. Create a sketch

### c. Make a draft of your visualization

### d. Write an artist statement

## Problem 3. Statistical critique

### a. Revisit and summarize

### b. Visual clarity

### c. Aesthetic clarity

### d. Recommendations
