---
title: " ENVS-193DS Homework 03"
author: Monique Hernandez
format: html
---

[GitHub Repository](https://github.com/moniqueallyson/ENVS-193DS_homework-03.git)

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(gt)
library(janitor)
library(here)
library(dplyr)
mydata <- read.csv("/Users/moniquehernandez/Desktop/ENVS-193DS/assignment/hw-03/ENVS HW 3/data/Data.csv") |> 
  clean_names()
```

## Problem 1. Personal Data

### a. Data summarizing

I could do the mean pain level after each day to analyze if there is a comparison between the days I do yoga and the days I don't do yoga. between the days I do and don't yoga. Though, there aren't any changes for the days I don't practice yoga, so I could calculate the change in pain on days I do practice such as subtracting the pain before from the pain after to measure if yoga does help chronic pain.

### b. Visualization

```{r}

#base layer: gg plot
ggplot(mydata, aes(x = did_you_do_yoga, # x-axis
                   y = pain_level_after)) + # y-axis
  geom_jitter(height = 0, # no vertical
              width = 0.15, # narrower jitter
              color = "violet") + # color for jitter
  # scond layer: point representing mean
  stat_summary(geom = "point", # geometry being plotted
               fun = mean, # function calculating the mean
               color = "pink", #  color for average
               size = 5) + # larger point size
labs(x = "Yoga Session", # labeling x-axis
     y= "Pain Scale After Yoga") + # labeling y-axis
theme_minimal()
```

### c. Caption

**Figure 1. Pain Level After a Yoga Session vs. No Session:** Individual pain level is shown as small violet jitter points to display distribution, while the mean pain level is shown as the larger pink point. Pain level is self-assessed on a pain scale from 1-10.

### d. Table presentation

```{r}

Pain_summary <-mydata |> # create new summary object from mydata
  group_by(did_you_do_yoga) |>
  summarize(
    mean_pain = round(mean(pain_level_after, na.rm = TRUE), 1), # calculate the mean
  )

Pain_summary |>
  gt() |>
  cols_label(
    did_you_do_yoga = "Yoga Session",
    mean_pain = "Mean Pain Level After (1-10)"
  ) |>
  tab_header(
    title = "Average Pain Levels After Yoga vs. No Yoga"
  )


```

## Problem 2. Affective visualization

### a. Describe affective visualization

The image of a dark, vast ocean with a small boat can depict the isolation of dealing with chronic pain as it can feel like a long lonely journey. There is a small streak of bright color in the sky depicting a light of hope, in this case the chronic pain can be manageable. The boat is more than the physical vessel, it is a metaphor for struggling to stay afloat on a daily basis.

### b. Create a sketch

### c. Make a draft of your visualization

### d. Write an artist statement

## Problem 3. Statistical critique

### a. Revisit and summarize

### b. Visual clarity

### c. Aesthetic clarity

### d. Recommendations
