---
title: "ENVS-193DS Homework 03"
author: Monique Hernandez
date: June 2, 2025
format:
  html:
    toc: true
    toc-location: right
    toc-depth: 3
---

[GitHub Repository](https://github.com/moniqueallyson/ENVS-193DS_homework-03.git)

```{r, message=FALSE, warning=FALSE}

# general use
library(tidyverse)
library(gt)
library(janitor)
library(here)
library(dplyr)

# reading in data
mydata <- read.csv("/Users/moniquehernandez/Desktop/ENVS-193DS/assignment/hw-03/ENVS HW 3/data/Data.csv") |> 
  clean_names()
```

## Problem 1. Personal Data

### a. Data summarizing

I could do the mean pain level after each day to analyze if there is a comparison between the days I do yoga and the days I don't do yoga. between the days I do and don't yoga. Though, there aren't any changes for the days I don't practice yoga, so I could calculate the change in pain on days I do practice such as subtracting the pain before from the pain after to measure if yoga does help chronic pain.

### b. Visualization

```{r}

#base layer: gg plot
ggplot(mydata, aes(x = did_you_do_yoga, # x-axis
                   y = pain_level_after)) + # y-axis
  geom_jitter(height = 0, # no vertical
              width = 0.15, # narrower jitter
              color = "violet") + # color for jitter
  # scond layer: point representing mean
  stat_summary(geom = "point", # geometry being plotted
               fun = mean, # function calculating the mean
               color = "pink", #  color for average
               size = 5) + # larger point size
labs(x = "Yoga Session", # labeling x-axis
     y= "Pain Scale After Yoga") + # labeling y-axis
theme_minimal()
```

### c. Caption

**Figure 1. Pain Level After a Yoga Session vs. No Session:** Individual pain level is shown as small violet jitter points to display distribution, while the mean pain level is shown as the larger pink point. Pain level is self-assessed on a pain scale from 1-10.

### d. Table presentation

```{r}

Pain_summary <-mydata |> # create new summary object from mydata
  group_by(did_you_do_yoga) |> # group by data whethere yoga was practiced or not
  summarize(
    mean_pain = round(mean(pain_level_after, na.rm = TRUE), 1), # calculate the mean pain level
  )

Pain_summary |> # use summarized data
  gt() |> # use gt to create a table
  cols_label(
    did_you_do_yoga = "Yoga Session", # rename column to Yoga Session from did you do yoga
    mean_pain = "Mean Pain Level After (1-10)" # rename mean pain to Mean Pain Level After 
  ) |>
  tab_header(
    title = "Average Pain Levels After Yoga vs. No Yoga" # add title on top of the table
  )


```

## Problem 2. Affective visualization

### a. Describe affective visualization

The image of a dark, vast ocean with a small boat can depict the isolation of dealing with chronic pain as it can feel like a long lonely journey. There is a small streak of bright color in the sky depicting a light of hope, in this case the chronic pain can be manageable. The boat is more than the physical vessel, it is a metaphor for struggling to stay afloat on a daily basis.

### b. Create a sketch



### c. Make a draft of your visualization



### d. Write an artist statement

**Content**: The painting depicts an intense snapshot of a boat out in the middle of the ocean during a stormy, dark night. The dark colors represent the bleakness of chronic pain, while the bright streak of color represents a sense of hope.

**Influence:** When doing this art piece, I thought of an impressionist style—capturing a moment and translating raw emotion into something that can be physically seen and understood by someone who may not feel chronic pain. It is an attempt to turn pain into art through a creative, hands-on approach.

**Form:** The artwork was made with acrylic on a small canvas using an array of colors including orange, red, yellow, and black.

**Process:** I had paint I wanted to use and thought this assignment could be a type of experiment to blend data science and visual art. It took roughly half an hour to an hour since the canvas is small.

## Problem 3. Statistical critique

### a. Revisit and summarize

### b. Visual clarity

### c. Aesthetic clarity

### d. Recommendations
