---
title: " ENVS-193DS Homework 03"
author: Monique Hernandez
format: html
---

[GitHub Repository](https://github.com/moniqueallyson/ENVS-193DS_homework-03.git)

```{r}
library(tidyverse)
library(gt)
library(janitor)
library(here)
mydata <- read.csv("/Users/moniquehernandez/Desktop/ENVS-193DS/assignment/hw-03/Data.csv")
```

## Problem 1. Personal Data

### a. Data Summarizing

I could do the mean pain level after each day to analyze if there is a comparison between the days I do yoga and the days I don't do yoga. between the days I do and don't yoga. Though, there aren't any changes for the days I don't practice yoga, so I could calculate the change in pain on days I do practice such as subtracting the pain before from the pain after to measure if yoga does help chronic pain.

### b. Visualization

```{r}

```

### c. Caption

### d. Table presentation

## Problem 2. Affective visualization

### a. Describe affective visualization

### b. Create a sketch

### c. Make a draft of your visualization

### d. Write an artist statement

## Problem 3. Statistical critique

### a. Revisit and summarize

### b. Visual clarity

### c. Aesthetic clarity

### d. Recommendations
